Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-25 JASA-template.tex
Updates from Overleaf

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
\begin{table}[ht]
\caption{Causal estimates obtained from different methods
for 6 different
numbers of observations.}\label{tab:causal}
\centering
\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
\begin{tabular}{l|rrrrrrrrrrr}
  \hline
 & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
  \hline
RBCE (low) & 3.22 & 3.54 & 3.30 & 3.66 & 3.77 & 3.80 & 3.85 & 3.89 & 3.90 & 3.91 & 3.89 \\ 
  RBCE (up) & 4.03 & 3.96 & 3.50 & 3.77 & 3.82 & 3.83 & 3.90 & 3.93 & 3.92 & 3.92 & 3.91 \\ 
  SSCE & -- & -- & -- & -- & -- & 4.24 & 4.11 & 3.99 & 4.00 & 4.00 & 3.99 \\ 
  BSSCE & -- & -- & -- & -- & -- & 4.02 & 4.01 & 4.01 & 4.01 & 4.01 & 4.01 \\ 
  BSSL & -0.23 & 4.07 & 6.80 & 4.05 & 4.00 & 4.00 & 4.01 & 3.98 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
\begin{tabular}{l|rrrrrrrrrrr}
  \hline
 & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
  \hline
RBCE (low) & 2.79 & 3.70 & 3.77 & 3.56 & 3.69 & 3.70 & 3.81 & 3.78 & 3.81 & 3.82 & 3.85 \\ 
  RBCE (up) & 3.65 & 4.01 & 3.96 & 3.82 & 3.90 & 3.86 & 3.92 & 3.89 & 3.91 & 3.88 & 3.91 \\ 
  SSCE & -- & -- & -- & -- & -- & 4.80 & 4.05 & 4.06 & 6.02 & 4.04 & 4.04 \\ 
  BSSCE & -- & -- & -- & -- & -- & 10.34 & 8.12 & 4.17 & 4.04 & 4.06 & 4.05 \\ 
  BSSL & -6.68 & 3.62 & 4.06 & 4.07 & 4.06 & 4.02 & 4.05 & 4.07 & 4.03 & 4.05 & 4.04 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}

>>>>

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Mar 25 09:52:08 2024
\begin{table}[ht]
\centering
\small
\begin{tabular}{r|ccccc|ccccc}
  \hline
 Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
  \hline
 & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
  \hline
25 & 3.06 & 4.18 & -- & -- & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
  30 & 3.47 & 4.31 & -- & -- & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
  35 & 3.24 & 3.53 & -- & -- & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
  40 & 3.61 & 3.83 & -- & -- & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
  45 & 3.80 & 3.87 & -- & -- & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
  50 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
  55 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
  60 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
  65 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
  70 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
  75 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
  80 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
  85 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
  90 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
  95 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
  100 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
  105 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
  110 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
  115 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
  120 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  125 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  130 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
  135 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
  140 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  145 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  150 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
  155 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
  160 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  165 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
  170 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
  175 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
  180 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  185 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  190 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  195 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  200 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}
\end{table}
\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}
